The \dealii Library, Version 9.7

### 2025-07-10 9.7/paper.tex
update contributor list

\todo[inline]{Add list of contributors}
\begin{quote}
\end{quote}
Their contributions are much appreciated!

>>>>

\todo[inline]{Add list of contributors}
\begin{quote}
%  authors removed:
%  Daniel       Arndt,
%  Wolfgang     Bangerth,
%  Bruno        Blais,
%  Marc         Fehling,
%  Rene         Gassmoeller,
%  Timo         Heister,
%  Luca         Heltai,
%  Martin       Kronbichler,
%  Matthias     Maier,
%  Peter        Muench,
%  Jean-Paul    Pelteret,
%  Bruno        Turcksin,
%  David        Wells,
Pasquale     Africa,
Henry        Arhin,
Maximilian   Bergbauer,
Alfredo      Buttari,
Bruna        Campos,
Nicholas     Cantrell,
Xiaoming     Cao,
Chayapol     Chaoveeraprasit,
Jerett       Cherry,
Dario        Coscia,
John         Coughlin,
Nikita       Daniliuk,
Crystal      Farris,
Marco        Feder,
Emmanuel     Ferdman,
Federico     Fernandez,
Olivier      Gaboriault,
Mohamad      Ghadban,
Mahdi        Gharehbaygloo,
Robin        Görmer,
Davit        Gyulamiryan,
Lóránt       Hadnagy,
Fernando     Herrera,
Robin        Hiniborch,
Quang        Hoang,
Jordan       Hoffart,
Sascha       Hofstetter,
Yimin        Jin,
Yann         Jobic,
Sean         Johnson,
Vaishnavi    Kale,
Sebastian    Kinnewig,
Andreas      Koch,
Jason        Landini,
Zhou         Lei,
Yingli       Li,
Nils         Margenberg,
Oreste       Marquis,
Ryan         Moulday,
Nils         Much,
Tileuzhan    Mukhamet,
Peter        Munch,
Wasim~Niyaz  Munshi,
Natalia      Nebulishvili,
Luz          Paz,
David        Pecoraro,
Davide       Polverino,
Sanjeeb      Poudel,
Guilhem      Poy,
Laura        Prieto~Saavedra,
Sebastian    Proell,
Andreas      Ritthaler,
Mayank       Sabharwal,
Sam          Scheuerman,
Magdalena    Schreter,
Richard      Schussnig,
Kyle         Schwiebert,
Marc         Secanell,
Qingyuan     Shi,
Wyatt        Smith,
Simon        Sticko,
Dominik      Still,
Edward       Terrell,
Jan~Philipp  Thiele,
Xiaochuan    Tian,
Siarhei      Uzunbajakau,
Mikael       Vaillant,
Vinayak      Vijay,
Stephan      Voss,
Michał       Wichrowski,
Simon        Wiesheier,
Yi-Yung      Yang,
\end{quote}
Their contributions are much appreciated!
